---
title: 'Results for age-specific/mobility renewal model -- new strain'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  job_tag:
    value: x
---
  
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, '-', name, ".png"))
file.to.rds = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag,'-', name, ".rds"))

```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with job tag
```{r, echo=FALSE}
args$job_tag
```

# Results

## Expected daily deaths {.tabset .tabset-fade}

### Total {.tabset .tabset-fade}

#### With rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))
}
```

`r if (file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))
}
```

#### Without rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-deaths_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))
}
```

`r if (file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-deaths_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))
}
```

### By strain {.tabset .tabset-fade}

#### With rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))
}
```

`r if (file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))
}
```

#### Without rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))
}
```

`r if (file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-deathsbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))
}
```



## Expected daily cases {.tabset .tabset-fade}

### Total {.tabset .tabset-fade}

#### With rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))
}
```

`r if (file.exists(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))
}
```

#### Without rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-cases_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))
}
```

`r if (file.exists(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-cases_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))
}
```


### By strain {.tabset .tabset-fade}

#### With rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))
}
```

`r if (file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))
}
```

#### Without rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))) '##### Schools stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-casesbystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))
}
```

`r if (file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))) '##### Schools close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("new-casesbystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))
}
```


## Expected reproduction number by age {.tabset .tabset-fade}

### With rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))) '#### School stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_TRUE"))
}
```

`r if (file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))) '#### School close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))){
  knitr::include_graphics(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_TRUE"))
}
```

### Without rebound mobility {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))) '#### School stay open'`

```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_TRUE_rebound_mobility_FALSE"))
}
```

`r if (file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))) '#### School close on 2021, Jan 1'`
```{r, out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))){
  knitr::include_graphics(file.to.figure("Rt_byage_bystrain_new_strain_school_closure_2_FALSE_rebound_mobility_FALSE"))
}
```


