---
title: 'Results for age-specific/mobility renewal model'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  job_tag:
    value: x
  states:
    value: x
---
  
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-", name, ".png"))
```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with job tag
```{r, echo=FALSE}
args$job_tag
```

## Results

### Expected deaths  {.tabset .tabset-fade}

`r if ('AL' %in% args$states) '#### Alabama'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-AL"))){
  knitr::include_graphics(file.to.figure("E_deathsByAge_panel-AL"))
}
```

`r if ('AK' %in% args$states) '#### Alaska'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-AK"))){
  knitr::include_graphics(file.to.figure("E_deathsByAge_panel-AK"))
}
```

`r if ('AZ' %in% args$states) '#### Arizona'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-AZ"))){
  knitr::include_graphics(file.to.figure("E_deathsByAge_panel-AZ"))
}
```

`r if ('AR' %in% args$states) '#### Arkansas'`
```{r, include=('AR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-AR"))){
  knitr::include_graphics(file.to.figure("E_deathsByAge_panel-AR"))
}
```

`r if ('CA' %in% args$states) '#### California'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-CA"))){
  knitr::include_graphics(file.to.figure("E_deathsByAge_panel-CA"))
}
```

`r if ('CO' %in% args$states) '#### Colorado'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-CO"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-CO"))
}
```

`r if ('CT' %in% args$states) '#### Connecticut'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-CT"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-CT"))
}
```

`r if ('DE' %in% args$states) '#### Delaware'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-DE"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-DE"))
}
```

`r if ('DC' %in% args$states) '#### District of Columbia'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-DC"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-DC"))
}
```

`r if ('FL' %in% args$states) '#### Florida'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-FL"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-FL"))
}
```

`r if ('GA' %in% args$states) '#### Georgia'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-GA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-GA"))
}
```

`r if ('HI' %in% args$states) '#### Hawaii'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-HI"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-HI"))
}
```

`r if ('ID' %in% args$states) '#### Indiana'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-ID"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-ID"))
}
```

`r if ('IL' %in% args$states) '#### Illinois'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-IL"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-IL"))
}
```

`r if ('IN' %in% args$states) '#### Indiana'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-IN"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-IN"))
}
```

`r if ('IA' %in% args$states) '#### Iowa'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-IA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-IA"))
}
```

`r if ('KS' %in% args$states) '#### Kansas'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-KS"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-KS"))
}
```

`r if ('KY' %in% args$states) '#### Kentucky'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-KY"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-KY"))
}
```

`r if ('LA' %in% args$states) '#### Louisiana'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-LA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-LA"))
}
```

`r if ('ME' %in% args$states) '#### Maine'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-ME"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-ME"))
}
```

`r if ('MD' %in% args$states) '#### Maryland'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MD"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MD"))
}
```

`r if ('MA' %in% args$states) '#### Massachusetts'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MA"))
}
```

`r if ('MI' %in% args$states) '#### Michigan'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MI"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MI"))
}
```

`r if ('MN' %in% args$states) '#### Minnesota'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MN"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MN"))
}
```

`r if ('MS' %in% args$states) '#### Mississippi'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MS"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MS"))
}
```

`r if ('MO' %in% args$states) '#### Missouri'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MO"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MO"))
}
```

`r if ('MT' %in% args$states) '#### Montana'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-MT"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-MT"))
}
```

`r if ('NE' %in% args$states) '#### Nebraska'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NE"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NE"))
}
```

`r if ('NV' %in% args$states) '#### Nevada'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NV"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NV"))
}
```

`r if ('NH' %in% args$states) '#### New Hampshire'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NH"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NH"))
}
```

`r if ('NJ' %in% args$states) '#### New Jersey'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NJ"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NJ"))
}
```

`r if ('NM' %in% args$states) '#### New Mexico'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NM"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NM"))
}
```

`r if ('NY' %in% args$states) '#### New York'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NY"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NY"))
}
```

`r if ('NYC' %in% args$states) '#### New York City'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NYC"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NYC"))
}
```

`r if ('NC' %in% args$states) '#### North Carolina'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-NC"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-NC"))
}
```

`r if ('ND' %in% args$states) '#### North Dakota'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-ND"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-ND"))
}
```

`r if ('OH' %in% args$states) '#### Ohio'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-OH"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-OH"))
}
```

`r if ('OK' %in% args$states) '#### Oklahoma'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-OK"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-OK"))
}
```

`r if ('OR' %in% args$states) '#### Oregon'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-OR"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-OR"))
}
```

`r if ('PA' %in% args$states) '#### Pennsylvania'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-PA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-PA"))
}
```

`r if ('RI' %in% args$states) '#### Rhode Island'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-RI"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-RI"))
}
```

`r if ('SC' %in% args$states) '#### South Carolina'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-SC"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-SC"))
}
```

`r if ('SD' %in% args$states) '#### South Dakota'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-SD"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-SD"))
}
```

`r if ('TN' %in% args$states) '#### Tennessee'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-TN"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-TN"))
}
```

`r if ('TX' %in% args$states) '#### Texas'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-TX"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-TX"))
}
```

`r if ('UT' %in% args$states) '#### Utah'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-UT"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-UT"))
}
```

`r if ('VT' %in% args$states) '#### Vermont'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-VT"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-VT"))
}
```

`r if ('VA' %in% args$states) '#### Virginia'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-VA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-VA"))
}
```

`r if ('WA' %in% args$states) '#### Washington'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-WA"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-WA"))
}
```

`r if ('WV' %in% args$states) '#### West Virginia'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-WV"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-WV"))
}
```

`r if ('WI' %in% args$states) '#### Wisconsin'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-WI"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-WI"))
}
```

`r if ('WY' %in% args$states) '#### Wyoming'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("E_deathsByAge_panel-WY"))){
knitr::include_graphics(file.to.figure("E_deathsByAge_panel-WY"))
}
```

### Summaries by state {.tabset .tabset-fade}

`r if ('AL' %in% args$states) '#### Alabama'`
`r if ('AL' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-AL"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-AL"))
}
```

`r if ('AL' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-AL"))){
  knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-AL"))
}
```

`r if ('AL' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-AL"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-AL"))
}
```

`r if ('AL' %in% args$states) '##### Flows between age bands'`
```{r, include=('AL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-AL")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-AL")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-AL"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-AL"),file.to.figure("reduced_flow_sourcesonwardabs-AL"),file.to.figure("reduced_flow_sourcesonwardprop-AL")))
}
```

`r if ('AK' %in% args$states) '#### Alaska'`
`r if ('AK' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-AK"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-AK"))
}
```

`r if ('AK' %in% args$states) '#### Evolution of contact intensities over time'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-AK"))){
  knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-AK"))
}
```

`r if ('AK' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-AK"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-AK"))
}
```

`r if ('AK' %in% args$states) '##### Flows between age bands'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-AK")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-AK")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-AK"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-AK"),file.to.figure("reduced_flow_sourcesonwardabs-AK"),file.to.figure("reduced_flow_sourcesonwardprop-AK")))
}
```


`r if ('AZ' %in% args$states) '#### Arizona'`
`r if ('AZ' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-AZ"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-AZ"))
}
```

`r if ('AZ' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-AZ"))){
  knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-AZ"))
}
```

`r if ('AZ' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-AZ"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-AZ"))
}
```

`r if ('AZ' %in% args$states) '##### Flows between age bands'`
```{r, include=('AZ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-AZ")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-AZ")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-AZ"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-AZ"),file.to.figure("reduced_flow_sourcesonwardabs-AZ"),file.to.figure("reduced_flow_sourcesonwardprop-AZ")))
}
```


`r if ('AK' %in% args$states) '#### Arkansas'`
`r if ('AK' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-AK"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-AK"))
}
```

`r if ('AK' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-AK"))){
  knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-AK"))
}
```

`r if ('AK' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-AK"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-AK"))
}
```

`r if ('AK' %in% args$states) '##### Flows between age bands'`
```{r, include=('AK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-AK")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-AK")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-AK"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-AK"),file.to.figure("reduced_flow_sourcesonwardabs-AK"),file.to.figure("reduced_flow_sourcesonwardprop-AK")))
}
```


`r if ('CA' %in% args$states) '#### California'`
`r if ('CA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-CA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-CA"))
}
```

`r if ('CA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-CA"))){
  knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-CA"))
}
```

`r if ('CA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-CA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-CA"))
}
```

`r if ('CA' %in% args$states) '##### Flows between age bands'`
```{r, include=('CA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-CA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-CA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-CA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-CA"),file.to.figure("reduced_flow_sourcesonwardabs-CA"),file.to.figure("reduced_flow_sourcesonwardprop-CA")))
}
```

`r if ('CO' %in% args$states) '#### Colorado'`
`r if ('CO' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-CO"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-CO"))
}
```

`r if ('CO' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-CO"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-CO"))
}
```

`r if ('CO' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('CO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-CO"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-CO"))
}
```

`r if ('CO' %in% args$states) '##### Flows between age bands'`
```{r, include=('CO' %in% args$states), out.width="70%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-CO")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-CO")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-CO"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-CO"),file.to.figure("reduced_flow_sourcesonwardabs-CO"),file.to.figure("reduced_flow_sourcesonwardprop-CO")))
}
```


`r if ('CT' %in% args$states) '#### Connecticut'`
`r if ('CT' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-CT"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-CT"))
}
```

`r if ('CT' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-CT"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-CT"))
}
```

`r if ('CT' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-CT"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-CT"))
}
```

`r if ('CT' %in% args$states) '##### Flows between age bands'`
```{r, include=('CT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-CT")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-CT")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-CT"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-CT"),file.to.figure("reduced_flow_sourcesonwardabs-CT"),file.to.figure("reduced_flow_sourcesonwardprop-CT")))
}
```


`r if ('DE' %in% args$states) '#### Delaware'`
`r if ('DE' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-DE"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-DE"))
}
```

`r if ('DE' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-DE"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-DE"))
}
```

`r if ('DE' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-DE"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-DE"))
}
```

`r if ('DE' %in% args$states) '##### Flows between age bands'`
```{r, include=('DE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-DE")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-DE")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-DE"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-DE"),file.to.figure("reduced_flow_sourcesonwardabs-DE"),file.to.figure("reduced_flow_sourcesonwardprop-DE")))
}
```


`r if ('DC' %in% args$states) '#### District of Columbia'`
`r if ('DC' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-DC"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-DC"))
}
```

`r if ('DC' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-DC"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-DC"))
}
```

`r if ('DC' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-DC"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-DC"))
}
```

`r if ('DC' %in% args$states) '##### Flows between age bands'`
```{r, include=('DC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-DC")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-DC")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-DC"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-DC"),file.to.figure("reduced_flow_sourcesonwardabs-DC"),file.to.figure("reduced_flow_sourcesonwardprop-DC")))
}
```


`r if ('FL' %in% args$states) '#### Florida'`
`r if ('FL' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-FL"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-FL"))
}
```

`r if ('FL' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-FL"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-FL"))
}
```

`r if ('FL' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-FL"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-FL"))
}
```

`r if ('FL' %in% args$states) '##### Flows between age bands'`
```{r, include=('FL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-FL")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-FL")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-FL"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-FL"),file.to.figure("reduced_flow_sourcesonwardabs-FL"),file.to.figure("reduced_flow_sourcesonwardprop-FL")))
}
```

`r if ('GA' %in% args$states) '#### Georgia'`
`r if ('GA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-GA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-GA"))
}
```

`r if ('GA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-GA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-GA"))
}
```

`r if ('GA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-GA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-GA"))
}
```

`r if ('GA' %in% args$states) '##### Flows between age bands'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-GA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-GA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-GA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-GA"),file.to.figure("reduced_flow_sourcesonwardabs-GA"),file.to.figure("reduced_flow_sourcesonwardprop-GA")))
}
```


`r if ('HI' %in% args$states) '#### Hawaii'`
`r if ('HI' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-HI"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-HI"))
}
```

`r if ('HI' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-HI"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-HI"))
}
```

`r if ('HI' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('HI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-HI"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-HI"))
}
```

`r if ('HI' %in% args$states) '##### Flows between age bands'`
```{r, include=('GA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-HI")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-HI")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-HI"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-HI"),file.to.figure("reduced_flow_sourcesonwardabs-HI"),file.to.figure("reduced_flow_sourcesonwardprop-HI")))
}
```

`r if ('ID' %in% args$states) '#### Idaho'`
`r if ('ID' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-ID"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-ID"))
}
```

`r if ('ID' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-ID"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-ID"))
}
```

`r if ('ID' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-ID"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-ID"))
}
```

`r if ('ID' %in% args$states) '##### Flows between age bands'`
```{r, include=('ID' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-ID")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-ID")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-ID"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-ID"),file.to.figure("reduced_flow_sourcesonwardabs-ID"),file.to.figure("reduced_flow_sourcesonwardprop-ID")))
}
```

`r if ('IL' %in% args$states) '#### Illinois'`
`r if ('IL' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-IL"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-IL"))
}
```

`r if ('IL' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-IL"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-IL"))
}
```

`r if ('IL' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-IL"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-IL"))
}
```

`r if ('IL' %in% args$states) '##### Flows between age bands'`
```{r, include=('IL' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-IL")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-IL")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-IL"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-IL"),file.to.figure("reduced_flow_sourcesonwardabs-IL"),file.to.figure("reduced_flow_sourcesonwardprop-IL")))
}
```


`r if ('IN' %in% args$states) '#### Indiana'`
`r if ('IN' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-IN"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-IN"))
}
```

`r if ('IN' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-IN"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-IN"))
}
```

`r if ('IN' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-IN"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-IN"))
}
```

`r if ('IN' %in% args$states) '##### Flows between age bands'`
```{r, include=('IN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-IN")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-IN")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-IN"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-IN"),file.to.figure("reduced_flow_sourcesonwardabs-IN"),file.to.figure("reduced_flow_sourcesonwardprop-IN")))
}
```


`r if ('IA' %in% args$states) '#### Iowa'`
`r if ('IA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-IA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-IA"))
}
```

`r if ('IA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-IA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-IA"))
}
```

`r if ('IA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-IA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-IA"))
}
```

`r if ('IA' %in% args$states) '##### Flows between age bands'`
```{r, include=('IA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-IA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-IA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-IA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-IA"),file.to.figure("reduced_flow_sourcesonwardabs-IA"),file.to.figure("reduced_flow_sourcesonwardprop-IA")))
}
```


`r if ('KS' %in% args$states) '#### Kansas'`
`r if ('KS' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-KS"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-KS"))
}
```

`r if ('KS' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-KS"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-KS"))
}
```

`r if ('KS' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-KS"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-KS"))
}
```

`r if ('KS' %in% args$states) '##### Flows between age bands'`
```{r, include=('KS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-KS")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-KS")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-KS"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-KS"),file.to.figure("reduced_flow_sourcesonwardabs-KS"),file.to.figure("reduced_flow_sourcesonwardprop-KS")))
}
```


`r if ('KY' %in% args$states) '#### Kentucky'`
`r if ('KY' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-KY"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-KY"))
}
```

`r if ('KY' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-KY"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-KY"))
}
```

`r if ('KY' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-KY"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-KY"))
}
```

`r if ('KY' %in% args$states) '##### Flows between age bands'`
```{r, include=('KY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-KY")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-KY")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-KY"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-KY"),file.to.figure("reduced_flow_sourcesonwardabs-KY"),file.to.figure("reduced_flow_sourcesonwardprop-KY")))
}
```

`r if ('LA' %in% args$states) '#### Louisiana'`
`r if ('LA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-LA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-LA"))
}
```

`r if ('LA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-LA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-LA"))
}
```

`r if ('LA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-LA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-LA"))
}
```

`r if ('LA' %in% args$states) '##### Flows between age bands'`
```{r, include=('LA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-LA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-LA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-LA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-LA"),file.to.figure("reduced_flow_sourcesonwardabs-LA"),file.to.figure("reduced_flow_sourcesonwardprop-LA")))
}
```


`r if ('ME' %in% args$states) '#### Maine'`
`r if ('ME' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-ME"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-ME"))
}
```

`r if ('ME' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-ME"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-ME"))
}
```

`r if ('ME' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-ME"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-ME"))
}
```

`r if ('ME' %in% args$states) '##### Flows between age bands'`
```{r, include=('ME' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-ME")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-ME")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-ME"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-ME"),file.to.figure("reduced_flow_sourcesonwardabs-ME"),file.to.figure("reduced_flow_sourcesonwardprop-ME")))
}
```


`r if ('MD' %in% args$states) '#### Maryland'`
`r if ('MD' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MD"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MD"))
}
```

`r if ('MD' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MD"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MD"))
}
```

`r if ('MD' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MD"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MD"))
}
```

`r if ('MD' %in% args$states) '##### Flows between age bands'`
```{r, include=('MD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MD")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MD")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MD"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MD"),file.to.figure("reduced_flow_sourcesonwardabs-MD"),file.to.figure("reduced_flow_sourcesonwardprop-MD")))
}
```

`r if ('MA' %in% args$states) '#### Massachusetts'`
`r if ('MA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MA"))
}
```

`r if ('MA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MA"))
}
```

`r if ('MA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MA"))
}
```

`r if ('MA' %in% args$states) '##### Flows between age bands'`
```{r, include=('MA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MA"),file.to.figure("reduced_flow_sourcesonwardabs-MA"),file.to.figure("reduced_flow_sourcesonwardprop-MA")))
}
```


`r if ('MI' %in% args$states) '#### Michigan'`
`r if ('MI' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MI"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MI"))
}
```

`r if ('MI' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MI"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MI"))
}
```

`r if ('MI' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MI"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MI"))
}
```

`r if ('MI' %in% args$states) '##### Flows between age bands'`
```{r, include=('MI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MI")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MI")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MI"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MI"),file.to.figure("reduced_flow_sourcesonwardabs-MI"),file.to.figure("reduced_flow_sourcesonwardprop-MI")))
}
```


`r if ('MN' %in% args$states) '#### Minnesota'`
`r if ('MN' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MN"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MN"))
}
```

`r if ('MN' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MN"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MN"))
}
```

`r if ('MN' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MN"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MN"))
}
```

`r if ('MN' %in% args$states) '##### Flows between age bands'`
```{r, include=('MN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MN")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MN")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MN"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MN"),file.to.figure("reduced_flow_sourcesonwardabs-MN"),file.to.figure("reduced_flow_sourcesonwardprop-MN")))
}
```

`r if ('MS' %in% args$states) '#### Mississippi'`
`r if ('MS' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MS"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MS"))
}
```

`r if ('MS' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MS"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MS"))
}
```

`r if ('MS' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MS"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MS"))
}
```

`r if ('MS' %in% args$states) '##### Flows between age bands'`
```{r, include=('MS' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MS")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MS")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MS"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MS"),file.to.figure("reduced_flow_sourcesonwardabs-MS"),file.to.figure("reduced_flow_sourcesonwardprop-MS")))
}
```


`r if ('MO' %in% args$states) '#### Missouri'`
`r if ('MO' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MO"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MO"))
}
```

`r if ('MO' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MO"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MO"))
}
```

`r if ('MO' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MO"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MO"))
}
```

`r if ('MO' %in% args$states) '##### Flows between age bands'`
```{r, include=('MO' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MO")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MO")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MO"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MO"),file.to.figure("reduced_flow_sourcesonwardabs-MO"),file.to.figure("reduced_flow_sourcesonwardprop-MO")))
}
```


`r if ('MT' %in% args$states) '#### Montana'`
`r if ('MT' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-MT"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-MT"))
}
```

`r if ('MT' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-MT"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-MT"))
}
```

`r if ('MT' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-MT"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-MT"))
}
```

`r if ('MT' %in% args$states) '##### Flows between age bands'`
```{r, include=('MT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-MT")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-MT")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-MT"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-MT"),file.to.figure("reduced_flow_sourcesonwardabs-MT"),file.to.figure("reduced_flow_sourcesonwardprop-MT")))
}
```


`r if ('NE' %in% args$states) '#### Nebraska'`
`r if ('NE' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NE"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NE"))
}
```

`r if ('NE' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NE"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NE"))
}
```

`r if ('NE' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NE"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NE"))
}
```

`r if ('NE' %in% args$states) '##### Flows between age bands'`
```{r, include=('NE' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NE")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NE")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NE"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NE"),file.to.figure("reduced_flow_sourcesonwardabs-NE"),file.to.figure("reduced_flow_sourcesonwardprop-NE")))
}
```


`r if ('NV' %in% args$states) '#### Nevada'`
`r if ('NV' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NV"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NV"))
}
```

`r if ('NV' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NV"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NV"))
}
```

`r if ('NV' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NV"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NV"))
}
```

`r if ('NV' %in% args$states) '##### Flows between age bands'`
```{r, include=('NV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NV")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NV")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NV"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NV"),file.to.figure("reduced_flow_sourcesonwardabs-NV"),file.to.figure("reduced_flow_sourcesonwardprop-NV")))
}
```


`r if ('NH' %in% args$states) '#### New Hampshire'`
`r if ('NH' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NH"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NH"))
}
```

`r if ('NH' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NH"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NH"))
}
```

`r if ('NH' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NH"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NH"))
}
```

`r if ('NH' %in% args$states) '##### Flows between age bands'`
```{r, include=('NH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NH")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NH")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NH"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NH"),file.to.figure("reduced_flow_sourcesonwardabs-NH"),file.to.figure("reduced_flow_sourcesonwardprop-NH")))
}
```


`r if ('NJ' %in% args$states) '#### New Jersey'`
`r if ('NJ' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NJ"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NJ"))
}
```

`r if ('NJ' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NJ"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NJ"))
}
```

`r if ('NJ' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NJ"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NJ"))
}
```

`r if ('NJ' %in% args$states) '##### Flows between age bands'`
```{r, include=('NJ' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NJ")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NJ")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NJ"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NJ"),file.to.figure("reduced_flow_sourcesonwardabs-NJ"),file.to.figure("reduced_flow_sourcesonwardprop-NJ")))
}
```


`r if ('NM' %in% args$states) '#### New Mexico'`
`r if ('NM' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NM"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NM"))
}
```

`r if ('NM' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NM"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NM"))
}
```

`r if ('NM' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NM"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NM"))
}
```

`r if ('NM' %in% args$states) '##### Flows between age bands'`
```{r, include=('NM' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NM")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NM")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NM"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NM"),file.to.figure("reduced_flow_sourcesonwardabs-NM"),file.to.figure("reduced_flow_sourcesonwardprop-NM")))
}
```


`r if ('NY' %in% args$states) '#### New York'`
`r if ('NY' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NY"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NY"))
}
```

`r if ('NY' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NY"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NY"))
}
```


`r if ('NY' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NY"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NY"))
}
```

`r if ('NY' %in% args$states) '##### Flows between age bands'`
```{r, include=('NY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NY")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NY")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NY"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NY"),file.to.figure("reduced_flow_sourcesonwardabs-NY"),file.to.figure("reduced_flow_sourcesonwardprop-NY")))
}
```


`r if ('NYC' %in% args$states) '#### New York City'`
`r if ('NYC' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NYC"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NYC"))
}
```

`r if ('NYC' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NYC"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NYC"))
}
```

`r if ('NYC' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NYC"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NYC"))
}
```

`r if ('NYC' %in% args$states) '##### Flows between age bands'`
```{r, include=('NYC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NYC")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NYC")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NYC"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NYC"),file.to.figure("reduced_flow_sourcesonwardabs-NYC"),file.to.figure("reduced_flow_sourcesonwardprop-NYC")))
}
```


`r if ('NC' %in% args$states) '#### North Carolina'`
`r if ('NC' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-NC"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-NC"))
}
```

`r if ('NC' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-NC"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-NC"))
}
```

`r if ('NC' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-NC"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-NC"))
}
```

`r if ('NC' %in% args$states) '##### Flows between age bands'`
```{r, include=('NC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-NC")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-NC")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-NC"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-NC"),file.to.figure("reduced_flow_sourcesonwardabs-NC"),file.to.figure("reduced_flow_sourcesonwardprop-NC")))
}
```


`r if ('ND' %in% args$states) '#### North Dakota'`
`r if ('ND' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-ND"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-ND"))
}
```

`r if ('ND' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-ND"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-ND"))
}
```

`r if ('ND' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-ND"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-ND"))
}
```

`r if ('ND' %in% args$states) '##### Flows between age bands'`
```{r, include=('ND' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-ND")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-ND")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-ND"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-ND"),file.to.figure("reduced_flow_sourcesonwardabs-ND"),file.to.figure("reduced_flow_sourcesonwardprop-ND")))
}
```


`r if ('OH' %in% args$states) '#### Ohio'`
`r if ('OH' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-OH"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-OH"))
}
```

`r if ('OH' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-OH"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-OH"))
}
```

`r if ('OH' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-OH"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-OH"))
}
```

`r if ('OH' %in% args$states) '##### Flows between age bands'`
```{r, include=('OH' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-OH")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-OH")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-OH"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-OH"),file.to.figure("reduced_flow_sourcesonwardabs-OH"),file.to.figure("reduced_flow_sourcesonwardprop-OH")))
}
```

`r if ('OK' %in% args$states) '#### Oklahoma'`
`r if ('OK' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-OK"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-OK"))
}
```

`r if ('OK' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-OK"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-OK"))
}
```

`r if ('OK' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-OK"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-OK"))
}
```

`r if ('OK' %in% args$states) '##### Flows between age bands'`
```{r, include=('OK' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-OK")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-OK")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-OK"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-OK"),file.to.figure("reduced_flow_sourcesonwardabs-OK"),file.to.figure("reduced_flow_sourcesonwardprop-OK")))
}
```

`r if ('OR' %in% args$states) '#### Oregon'`
`r if ('OR' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-OR"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-OR"))
}
```

`r if ('OR' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-OR"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-OR"))
}
```

`r if ('OR' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-OR"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-OR"))
}
```

`r if ('OR' %in% args$states) '##### Flows between age bands'`
```{r, include=('OR' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-OR")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-OR")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-OR"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-OR"),file.to.figure("reduced_flow_sourcesonwardabs-OR"),file.to.figure("reduced_flow_sourcesonwardprop-OR")))
}
```

`r if ('PA' %in% args$states) '#### Pennsylvania'`
`r if ('PA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-PA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-PA"))
}
```

`r if ('PA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-PA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-PA"))
}
```

`r if ('PA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-PA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-PA"))
}
```

`r if ('PA' %in% args$states) '##### Flows between age bands'`
```{r, include=('PA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-PA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-PA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-PA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-PA"),file.to.figure("reduced_flow_sourcesonwardabs-PA"),file.to.figure("reduced_flow_sourcesonwardprop-PA")))
}
```


`r if ('RI' %in% args$states) '#### Rhode Island'`
`r if ('RI' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-RI"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-RI"))
}
```

`r if ('RI' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-RI"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-RI"))
}
```

`r if ('RI' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-RI"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-RI"))
}
```

`r if ('RI' %in% args$states) '##### Flows between age bands'`
```{r, include=('RI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-RI")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-RI")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-RI"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-RI"),file.to.figure("reduced_flow_sourcesonwardabs-RI"),file.to.figure("reduced_flow_sourcesonwardprop-RI")))
}
```


`r if ('SC' %in% args$states) '#### South Carolina'`
`r if ('SC' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-SC"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-SC"))
}
```

`r if ('SC' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-SC"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-SC"))
}
```

`r if ('SC' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-SC"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-SC"))
}
```

`r if ('SC' %in% args$states) '##### Flows between age bands'`
```{r, include=('SC' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-SC")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-SC")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-SC"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-SC"),file.to.figure("reduced_flow_sourcesonwardabs-SC"),file.to.figure("reduced_flow_sourcesonwardprop-SC")))
}
```


`r if ('SD' %in% args$states) '#### South Dakota'`
`r if ('SD' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-SD"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-SD"))
}
```

`r if ('SD' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-SD"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-SD"))
}
```

`r if ('SD' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-SD"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-SD"))
}
```

`r if ('SD' %in% args$states) '##### Flows between age bands'`
```{r, include=('SD' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-SD")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-SD")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-SD"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-SD"),file.to.figure("reduced_flow_sourcesonwardabs-SD"),file.to.figure("reduced_flow_sourcesonwardprop-SD")))
}
```


`r if ('TN' %in% args$states) '#### Tennessee'`
`r if ('TN' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-TN"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-TN"))
}
```

`r if ('TN' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-TN"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-TN"))
}
```

`r if ('TN' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-TN"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-TN"))
}
```

`r if ('TN' %in% args$states) '##### Flows between age bands'`
```{r, include=('TN' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-TN")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-TN")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-TN"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-TN"),file.to.figure("reduced_flow_sourcesonwardabs-TN"),file.to.figure("reduced_flow_sourcesonwardprop-TN")))
}
```


`r if ('TX' %in% args$states) '#### Texas'`
`r if ('TX' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-TX"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-TX"))
}
```

`r if ('TX' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-TX"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-TX"))
}
```

`r if ('TX' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-TX"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-TX"))
}
```

`r if ('TX' %in% args$states) '##### Flows between age bands'`
```{r, include=('TX' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-TX")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-TX")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-TX"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-TX"),file.to.figure("reduced_flow_sourcesonwardabs-TX"),file.to.figure("reduced_flow_sourcesonwardprop-TX")))
}
```


`r if ('UT' %in% args$states) '#### Utah'`
`r if ('UT' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-UT"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-UT"))
}
```

`r if ('UT' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-UT"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-UT"))
}
```

`r if ('UT' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-UT"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-UT"))
}
```

`r if ('UT' %in% args$states) '##### Flows between age bands'`
```{r, include=('UT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-UT")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-UT")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-UT"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-UT"),file.to.figure("reduced_flow_sourcesonwardabs-UT"),file.to.figure("reduced_flow_sourcesonwardprop-UT")))
}
```


`r if ('VT' %in% args$states) '#### Vermont'`
`r if ('VT' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-VT"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-VT"))
}
```

`r if ('VT' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-VT"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-VT"))
}
```

`r if ('VT' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-VT"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-VT"))
}
```

`r if ('VT' %in% args$states) '##### Flows between age bands'`
```{r, include=('VT' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-VT")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-VT")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-VT"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-VT"),file.to.figure("reduced_flow_sourcesonwardabs-VT"),file.to.figure("reduced_flow_sourcesonwardprop-VT")))
}
```

`r if ('VA' %in% args$states) '#### Virginia'`
`r if ('VA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-VA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-VA"))
}
```

`r if ('VA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-VA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-VA"))
}
```

`r if ('VA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-VA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-VA"))
}
```

`r if ('VA' %in% args$states) '##### Flows between age bands'`
```{r, include=('VA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-VA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-VA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-VA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-VA"),file.to.figure("reduced_flow_sourcesonwardabs-VA"),file.to.figure("reduced_flow_sourcesonwardprop-VA")))
}
```

`r if ('WA' %in% args$states) '#### Washington'`
`r if ('WA' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-WA"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-WA"))
}
```

`r if ('WA' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-WA"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-WA"))
}
```

`r if ('WA' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-WA"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-WA"))
}
```

`r if ('WA' %in% args$states) '##### Flows between age bands'`
```{r, include=('WA' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-WA")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-WA")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-WA"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-WA"),file.to.figure("reduced_flow_sourcesonwardabs-WA"),file.to.figure("reduced_flow_sourcesonwardprop-WA")))
}
```


`r if ('WV' %in% args$states) '#### West Virginia'`
`r if ('WV' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-WV"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-WV"))
}
```

`r if ('WV' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-WV"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-WV"))
}
```

`r if ('WV' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-WV"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-WV"))
}
```

`r if ('WV' %in% args$states) '##### Flows between age bands'`
```{r, include=('WV' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-WV")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-WV")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-WV"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-WV"),file.to.figure("reduced_flow_sourcesonwardabs-WV"),file.to.figure("reduced_flow_sourcesonwardprop-WV")))
}
```


`r if ('WI' %in% args$states) '#### Wisconsin'`
`r if ('WI' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-WI"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-WI"))
}
```

`r if ('WI' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-WI"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-WI"))
}
```

`r if ('WI' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-WI"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-WI"))
}
```

`r if ('WI' %in% args$states) '##### Flows between age bands'`
```{r, include=('WI' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-WI")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-WI")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-WI"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-WI"),file.to.figure("reduced_flow_sourcesonwardabs-WI"),file.to.figure("reduced_flow_sourcesonwardprop-WI")))
}
```

`r if ('WY' %in% args$states) '#### Wyoming'`
`r if ('WY' %in% args$states) '##### Daily cases, daily deaths and Rt in the population'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("cases_deaths_Rt_panel_plot-WY"))){
  knitr::include_graphics(file.to.figure("cases_deaths_Rt_panel_plot-WY"))
}
```

`r if ('WY' %in% args$states) '##### Evolution of contact intensities over time'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("deaths_mobilitytrends_contactpatterns-WY"))){
knitr::include_graphics(file.to.figure("deaths_mobilitytrends_contactpatterns-WY"))
}
```

`r if ('WY' %in% args$states) '##### Rt, expected cases, attack rate, infectious contacts by age band'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("five_panel_plot_new-WY"))){
knitr::include_graphics(file.to.figure("five_panel_plot_new-WY"))
}
```

`r if ('WY' %in% args$states) '##### Flows between age bands'`
```{r, include=('WY' %in% args$states), out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(all(c(file.exists(file.to.figure("flow_summary-WY")),file.exists(file.to.figure("reduced_flow_sourcesonwardabs-WY")),file.exists(file.to.figure("reduced_flow_sourcesonwardprop-WY"))))){
knitr::include_graphics(c(file.to.figure("flow_summary-WY"),file.to.figure("reduced_flow_sourcesonwardabs-WY"),file.to.figure("reduced_flow_sourcesonwardprop-WY")))
}
```

### IFR and attack rate by state
```{r, include=TRUE, out.width="100%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("ifroverall-bystate"))){
knitr::include_graphics(file.to.figure("ifroverall-bystate"))
}
```

```{r, include=TRUE, out.width="100%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("attackrateoverall-bystate"))){
knitr::include_graphics(file.to.figure("attackrateoverall-bystate"))
}
```

### Parameter estimates  {.tabset .tabset-fade}

#### State-specific parameters

```{r, include=TRUE, out.width="120%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("model_parameters_all_states"))){
knitr::include_graphics(file.to.figure("model_parameters_all_states"))
}
```

#### Age-specific parameters
##### IFR by age
```{r, include=TRUE, out.width="40%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("ifr_age_base"))){
knitr::include_graphics(file.to.figure("ifr_age_base"))
}
```

```{r, include=TRUE, out.width="50%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("log_ifr_age_base_prior_posterior"))){
knitr::include_graphics(file.to.figure("log_ifr_age_base_prior_posterior"))
}
```

```{r, include=TRUE, out.width="60%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("log_ifr_age_prior_posterior_1"))){
knitr::include_graphics(file.to.figure("log_ifr_age_prior_posterior_1"))
}
```

```{r, include=TRUE, out.width="60%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("log_ifr_age_prior_posterior_2"))){
knitr::include_graphics(file.to.figure("log_ifr_age_prior_posterior_2"))
}
```

##### Age shift
```{r, include=TRUE, out.width="60%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("timeeff_shift_age"))){
knitr::include_graphics(file.to.figure("timeeff_shift_age"))
}
```

##### Susceptibility by age
###### Posterior
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("relsusceptibility_age"))){
knitr::include_graphics(file.to.figure("relsusceptibility_age"))
}
```

###### Standard deviation of log susceptibiity
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("sd_log_relsusceptibility_age"))){
knitr::include_graphics(file.to.figure("sd_log_relsusceptibility_age"))
}
```

##### Transmissibility by age
###### Posterior
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("reltransmissibility_age"))){
knitr::include_graphics(file.to.figure("reltransmissibility_age"))
}
```

###### Standard deviation of log susceptibiity
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("sd_log_reltransmissibility_age"))){
knitr::include_graphics(file.to.figure("sd_log_reltransmissibility_age"))
}
```

#### Other parameters
##### Mobility trend regression coefficients
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("beta"))){
knitr::include_graphics(file.to.figure("beta"))
}
```

##### Variance of state-specific R0
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("kappa"))){
knitr::include_graphics(file.to.figure("kappa"))
}
```

##### Overdispersion parameter in Neg Binomial model
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("phi"))){
knitr::include_graphics(file.to.figure("phi"))
}
```

#### Upswing space time random effects
##### Spatial effects
```{r, include=TRUE, out.width="40%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("upswing_rnde_density"))){
knitr::include_graphics(file.to.figure("upswing_rnde_density"))
}
```

##### Time effects
```{r, include=TRUE, out.width="80%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("upswing_timeeff_reduced"))){
knitr::include_graphics(file.to.figure("upswing_timeeff_reduced"))
}
```
```{r, include=TRUE, out.width="80%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("sd_upswing_timeeff_reduced"))){
knitr::include_graphics(file.to.figure("sd_upswing_timeeff_reduced"))
}
```


#### School attack rates
```{r,echo = FALSE}
file <- file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-","summary-attackrate-school.RDS") )
if(file.exists(file)){
  attackrate_school <- readRDS(file)
  kable(attackrate_school,caption = 'school attack rate')
}
```

#### Sampler diagnostics
```{r, echo = FALSE}
file <- file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-","sampler_diagnostics.rds") )
if(file.exists(file)){
  diagostics <- readRDS(file)
  diagostics
}
```

#### Convergence diagnostics
We present below the parameters which had a smaller effective sample size than 500, with their corresponding mean, standard deviation, n eff and R hat.

```{r, echo = FALSE}
file <- file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-","pars-with-small-neff.rds") )
if(file.exists(file)){
  neff <- readRDS(file)
  neff[which(neff[,9]<500), c(1, 2, 9, 10)]
}
```

### Effect of age-specific mobility trends on changes in baseline contact intensities

```{r, include=TRUE, out.width="120%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("eta_mtc-all-states"))){
knitr::include_graphics(file.to.figure("eta_mtc-all-states"))
}
```

```{r, include=TRUE, out.width="120%",  fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("marginal-contacts-overall-all-states"))){
knitr::include_graphics(file.to.figure("marginal-contacts-overall-all-states"))
}
```
