---
title: 'Results for age-specific/mobility renewal model'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  job_tag:
    value: x
  states:
    value: x
---
  
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-", name, ".png"))
file.to.rds = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-", name, ".rds"))
```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with job tag
```{r, echo=FALSE}
args$job_tag
```

## Results

### Expected forecasted deaths {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_20_level_K5"))) '#### 0.2'`
```{r, out.width="100%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_20_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_20_level_K5"))
}
```

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_33_level_K5"))) '#### 0.33'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_33_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_33_level_K5"))
}
```

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_50_level_K5"))) '#### 0.5'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_50_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_50_level_K5"))
}
```

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))) '#### 1.0'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))
}
```


### Expected contribution {.tabset .tabset-fade}

For a forecast period from
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))
  print(ans[[3]])
}
if(!file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))& file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5")) ){
   ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))
  print(ans[[3]])
}
```
to
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))
  print(ans[[4]])
}
if(!file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))& file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5")) ){
   ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))
  print(ans[[4]])
}
```

#### Under school closure scenario
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))
  knitr::kable(ans[[1]])
}
if(!file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))& file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5")) ){
   ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))
   knitr::kable(ans[[1]])
}
```


#### Under school re-opening scenario with school re-opening multiplier {.tabset .tabset-fade}
`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_20_level_K5"))) '##### 0.2'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_20_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_20_level_K5"))
  knitr::kable(ans[[2]])
}
```

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_33_level_K5"))) '##### 0.33'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_33_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_33_level_K5"))
  knitr::kable(ans[[2]])
}
```

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))) '##### 0.5'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_50_level_K5"))
  knitr::kable(ans[[2]])
}
```

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))) '##### 1.0'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))
  knitr::kable(ans[[2]])
}
```


### Excess COVID-19 infection and mortality  {.tabset .tabset-fade}

For a forecast period from
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))
  print(ans[[2]])
}
if(!file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))& file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5")) ){
   ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5"))
  print(ans[[2]])
}
```
to
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))){
  print(ans[[3]])
}
if(!file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))& file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5")) ){
   ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5"))
  print(ans[[3]])
}
```

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_20_level_K5"))) '#### 0.2'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_20_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_20_level_K5"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_33_level_K5"))) '#### 0.33'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_33_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_33_level_K5"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5"))) '#### 0.5'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_50_level_K5"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))) '#### 1.0'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))
    tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```

