---
title: 'Results for age-specific/mobility renewal model'
output:
  html_document: 
    default
params:
  stanModelFile:
    value: x
  job_dir:
    value: x
  job_tag:
    value: x
---
  
```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
args = params
file.to.figure = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-", name, ".png"))
file.to.rds = function(name) file.path(args$job_dir, paste0(args$stanModelFile, "-",args$job_tag, "-", name, ".rds"))

```

## Session info
This file presents the results of Stan model 
```{r, echo=FALSE}
args$stanModelFile
```
with job tag
```{r, echo=FALSE}
args$job_tag
```

# Results

## Expected forecasted deaths {.tabset .tabset-fade}
With school re-opening multiplier 


### Forecast

#### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))) '##### K5'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K5"))
}
```

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K12"))) '##### K12'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K12"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K12"))
}
```

### Counterfactual

#### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_1_multiplier_100_level_K5"))) '##### K5'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_1_multiplier_100_level_K5"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_1_multiplier_100_level_K5"))
}
```

`r if (file.exists(file.to.figure("new_deaths-forecast_counterfactual_0_multiplier_100_level_K12"))) '##### K12'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.figure("new_deaths-forecast_counterfactual_1_multiplier_100_level_K12"))){
  knitr::include_graphics(file.to.figure("new_deaths-forecast_counterfactual_1_multiplier_100_level_K12"))
}
```


## Expected contribution {.tabset .tabset-fade}

For a forecast period from
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))
  print(ans[[3]])
}

```
to
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))
  print(ans[[4]])
}
```

### Under school closure scenario
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12")) ){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))
  knitr::kable(ans[[1]])
}

```


### Under school re-opening scenario {.tabset .tabset-fade}

#### Forecast

##### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))) '###### K5'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K5"))
  knitr::kable(ans[[2]])
}
```

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))) '###### K12'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_0_multiplier_100_level_K12"))
  knitr::kable(ans[[2]])
}
```

#### Counterfactual

##### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K5"))) '###### K5'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K5"))
  knitr::kable(ans[[2]])
}
```

`r if (file.exists(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K12"))) '###### K12'`
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("flow-onward-forecast_counterfactual_1_multiplier_100_level_K12"))
  knitr::kable(ans[[2]])
}
```


## Excess COVID-19 infection and mortality {.tabset .tabset-fade}

For a forecast period from
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))
  print(ans[[2]])
}

```
to
```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))
  print(ans[[3]])
}

```

### Forecast

#### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))) '##### K5'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K5"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```


`r if (file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))) '##### K12'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_0_multiplier_100_level_K12"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```




### Counterfactual

#### School closed until level {.tabset .tabset-fade}

`r if (file.exists(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K5"))) '##### K5'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K5"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K5"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```



`r if (file.exists(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K12"))) '##### K12'`

```{r, out.width="120%", fig.show='hold', fig.align='centre', echo=FALSE}
if(file.exists(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K12"))){
  ans = readRDS(file.to.rds("excess-forecast_counterfactual_1_multiplier_100_level_K12"))
  tmp = rbind( t(c("",
                 "SARS-CoV-2 infections, closure scenario, (number)","Excess SARS-CoV-2 infections, re-opening scenario, (percent increase)", "Excess SARS-CoV-2 infections, re-opening scenario, (difference)",
                 "COVID-19 attributable deaths, closure scenario, (number)","Excess COVID-19 attributable deaths, re-opening scenario (percent increase)","Excess COVID-19 attributable deaths, re-opening scenario, (difference)")), as.matrix(ans[[1]]))
  knitr::kable(tmp)
}
```



